### 2020-04-30 README.Rmd
Explain map colours

<!-- We filtered-out roads with low levels of cycling potential and focus only on roads that have at least one 'spare lane', defined as having more than 1 lane in either direction. -->
Roads that could be made oneway, or that could be converted into 'liveable streets' by preventing through traffic have not been considered at this stage.
Providing evidence to identify such roads, e.g. where there is high demand but little road width, suggesting a strong argument for making them one-way during a period of vital physical distancing, in addition to the roads with 'spare lanes' identified below, could be an aim of future work.

>>>>

# Interpreting the results

The results are not intended to be a definitive list of places where popup cycleways should be prioritised.
There may be 'false positives' where there are strong reasons for not converting a 'spare lane' into a cycleway or temporary pavement.
There will be many road sections that would benefit from interventions not shown in the maps below: roads with only one lane in each direction could be made oneway temporarily, creating a spare lane for cycleways or extra pavement width.

<!-- We filtered-out roads with low levels of cycling potential and focus only on roads that have at least one 'spare lane', defined as having more than 1 lane in either direction. -->
Such roads and roads that could be converted into 'liveable streets' by preventing through traffic have not been considered at this stage.
Providing evidence to identify such roads, e.g. where there is high demand but little road width, suggesting a strong argument for making them one-way during a period of vital physical distancing, in addition to the roads with 'spare lanes' identified below, could be an aim of future work.

## What the maps show

The results below show all roads with a 'spare lane' in the low average traffic conditions created by the partial lockdown (light blue) plus the top 10 roads of a minimum length in terms of estimated cycling potential under the Government Target scenario in the PCT.
